\section{Changes}

\begin{multicols}{2}

\par Here are the changes I've made to the official rules of Blood Bowl, many of which are derived from the work of Phil Bowen back in the days of LRB4. They are almost all in the name of reduced complexity; so there are marginally fewer teams, fewer skills, and a balanced, portable, perpetual league system.
\par The Sevens rules are based heavily on the work of Russell Drysdale and Stephen Babbage.

\begin{itemize}
\item The league works on a Balanced Team Value system, so no bank/petty cash/spiralling expenses/gate rolls/whatever.
\item No inducements, which includes:
\item No Star Players. With the recent rule changes to allow rostering Stars, I may reconsider this.
\item Multiple permanent Apothecaries, rather than inducing Wanderers.
\item No Wizards. Ugh.
\item Balanced Team Value makes Necromancers redundant.
\item No Fan Factor, FAME, Cheerleaders or Assistant Coaches.
\item No Special Play cards.
\item No Weather conditions.
\item Simpler accrual of SPPs, in a way that spreads them around the team to avoid silly stats gamesmanship.
\item No characteristic increases.
\item No Goblin teams. This avoids most of the terrible Secret Weapon rules and, I think, removes any real balancing need for Bribes, so no Bribes either. To get rid of the last of the Secret Weapons, no Dwarf Deathroller (since I mostly play Sevens anyway).
\item No Halfling, Nurgle, Ogre, Vampire, Chaos Pact or Underworld teams, either because I find their rules too complicated, or just because they're unlikely to get chosen by the newish players in my time-bereft league. As an associated bonus, no real need for Master Chefs.
\item On the upside (?) I added Brettonians from the NAF's unofficial races.
\item I took Throw Team-Mate off the Human Ogre and the Wood Elf Treeman since there are no Star Players to throw. I saw no need to adjust their price as a result.
\item Several skills have been removed as a result of these changes (or in some cases, these changes were made specifically to remove what I consider burdensome skills): Animosity, Ball \& Chain, Blood Lust, Bombardier, Chainsaw, Fan Favourite, Hypnotic Gaze, No Hands, Nurgle's Rot, Pass Block, Piling On, Secret Weapon, Stakes, and Titchy.
\item ClawPOMB is nerfed by the removal of Piling On, as well as by GW's 2016 change to Claws (which they consider an erratum but I do not).
\item You could make a solid argument that Throw Team-Mate and its associates are the most burdensome rules of all, but a) the complexity only really affects the user, and they deserve everything they get, and b) they're just too strong a part of the Blood Bowl theme to remove. My hypocrisy knows no bounds.
\item The Sevens rules use the same pitch size as the official GW/NAF Sevens, but adopt almost the same ruleset as Drysdale Sevens in other respects. This allows the game to function as a much faster, more faithful version of core Blood Bowl rather than having the "everyone's an amateur" conceit of GW/NAF, and avoiding the dual line of scrimmage oddity.
\end{itemize}

\end{multicols}
