\section{Skills}
\par This section of the rules lists all the skills players can use. The specific rules for each skill are listed, as well as which category the skill belongs to. A skill's category affects which players can access it. Unless otherwise stated in the skill description, the following rules apply to all skills:

\begin{itemize}
\item All bonuses/modifiers from skills can be combined.
\item All skills may be used an unlimited number of times per Action.
\item Some skills refer to pushing a player back in order to work. These skills will work as long as you roll a result of 'Pushed', 'Defender Stumbles', or 'Defender Down' on the Block dice.
\item Skill use is not mandatory.
\item You can choose to use a skill that affects a dice roll after rolling the dice (e.g. Diving Tackle does not need to be used until after seeing the result of the Dodge roll).
\item Only Extraordinary skills work when a player is Prone or Stunned.
\item A skill may only be taken once per player.
\end{itemize}

\subsection{Skills by name}

\begin{multicols}{3}

\subsubsection{Accurate (Passing)}
\par This player may add 1 to the D6 roll when they pass the ball.

\subsubsection{Always Hungry (Extraordinary)}
\par Affects the use of the Throw Team-Mate skill.

\subsubsection{Big Hand (Mutation)}
\par This player ignores modifiers for enemy tackle zones when attempting to pick up the ball.

\subsubsection{Block (General)}
\par Affects the results rolled with the Block dice.

\subsubsection{Bonehead (Extraordinary)}
\par Roll a D6 immediately after declaring an Action for this player. On a roll of 1 the player can't do anything for the turn, and the player's team loses the declared Action for the turn. The player loses their tackle zones and may not catch, intercept, pass, assist on blocks or fouls, or voluntarily move until they manage a successful Bonehead roll at the start of a future Action.

\subsubsection{Break Tackle (Strength)}
\par This player may use their Strength instead of their Agility when making a Dodge roll. This skill may only be used once per turn.

\subsubsection{Catch (Agility)}
\par This player is allowed to re-roll the D6 if they fail a catch, drop a hand-off or fail to make an interception.

\subsubsection{Claws (Mutation)}
\par When an opponent is Knocked Down by this player during a block, any Armour roll of 8 or more after modifications automatically breaks armour.

\subsubsection{Dauntless (General)}
\par This skill only works when the player attempts to block an opponent who is stronger than himself. The coach of the player with the Dauntless skill rolls a D6 and adds it to their strength. If the total is equal to or lower than the opponent's Strength, the player must block using their normal Strength. If the total is greater, then the player with the Dauntless skill counts as having a Strength equal to their opponent's when they make the block. The strength of both players is calculated before any defensive or offensive assists are added but after all other modifiers.

\subsubsection{Decay (Extraordinary)}
\par When this player suffers a Casualty, roll twice on the Casualty table and apply both results. The player will only ever miss one match as a result. A successful Regeneration roll will heal both results.

\subsubsection{Dirty Player (General)}
\par Add 1 to the Armour roll or the Injury roll when this player makes a Foul. You may only modify one of the dice rolls.

\subsubsection{Disturbing Presence (Mutation)}
\par For each opposing player with Disturbing Presence within three squares (regardless of whether these players are Prone or Stunned), a player must subtract 1 from their Agility roll when they pass, intercept or catch.

\subsubsection{Diving Catch (Agility)}
\par This player may add 1 to any catch roll from an accurate pass targeted to their square. In addition, they can attempt to catch any pass, kick off or throw-in (but not bouncing ball), that would land in an empty adjacent square, as though it had landed in their own square. A failed catch will bounce from the Diving Catch player's square. If there are two or more players attempting to use this skill then they get in each other's way and neither can use it.

\subsubsection{Diving Tackle (Agility)}
\par The player may use this skill after an opposing player attempts to dodge out of any of their tackle zones. The player using this skill is placed Prone in the square vacated by the dodging player, but do not make an Armour or Injury roll for them. The opposing player must subtract 2 from their Dodge roll. Only one player may use Diving Tackle on a dodge. Diving Tackle may be used on a re-rolled dodge even if not declared for use on the first Dodge roll.

\subsubsection{Dodge (Agility)}
\par This player may re-roll the D6 if they fail to dodge out of an opposing player's tackle zones. The player may only re-roll one failed Dodge roll per turn. In addition, the Dodge skill, if used, affects the results rolled on the Block dice.

\subsubsection{Dump-Off (Passing)}
\par This skill allows the player to make a Quick Pass when an opponent declares that they will throw a block at them, allowing the player to get rid of the ball before they are hit. Work out the Dump-Off pass before the opponent makes their block. The normal throwing rules apply, except that neither team's turn ends as a result of the throw, whatever it may be. After the throw is worked out your opponent completes the block, and then carries on with their turn. Dump-Off may not be used on the second block from an opponent with the Frenzy skill or in conjunction with the Throw Team-Mate skill.

\subsubsection{Extra Arms (Mutation)}
\par Add 1 to any attempt to pick up, catch or intercept the ball.

\subsubsection{Fend (General)}
\par Opposing players may not follow-up blocks made against this player, even if they are Knocked Down. The opposing player may still continue moving after blocking if they had declared a Blitz Action.

\subsubsection{Foul Appearance (Mutation)}
\par Any opposing player that wants to block this player (or use a special attack that takes the place of a block) must first roll 2+ on a D6. If they roll a 1, they are too revolted to make the block and it is wasted (though their team does not suffer a turnover).

\subsubsection{Frenzy (General)}
\par Unless otherwise overridden, this skill must always be used. When making a block, this player must always follow up if they can. If a 'Pushed' or 'Defender Stumbles' result was chosen, they must immediately throw a second block (which must also be followed up) against the same opponent so long as they are both still standing and adjacent. If the frenzied player is performing a Blitz Action then they must make the second block unless they have no further MA and cannot Go For It again.

\subsubsection{Grab (Strength)}
\par If this player's block results in a push back they may choose any empty square adjacent to their opponent into which to push them. If there are no empty squares, or if the opponent has Side Step, the standard pushback rules apply. Grab will not work if there are no empty adjacent squares. A player with the Grab skill can never gain the Frenzy skill, and vice versa.

\subsubsection{Guard (Strength)}
\par This player assists an offensive or defensive block even if they are in another player's tackle zone. This skill may not be used to assist a foul.

\subsubsection{Hail Mary Pass (Passing)}
\par This player may throw the ball to any square on the playing pitch, no matter the range. First, roll a D6; on a roll of 1 the pass is fumbled. A successful Hail Mary pass may not be intercepted, but it is never accurate – the ball automatically misses and scatters three squares. This skill may not be used with the Throw Team-Mate skill.

\subsubsection{Horns (Mutation)}
\par Add 1 to this player's Strength for any blocks they make during a Blitz Action.

\subsubsection{Juggernaut (Strength)}
\par When this player makes a Blitz Action, they may choose to treat a 'Both Down' result as if a 'Pushed' result has been rolled instead, and opposing players may not use their Fend, Stand Firm or Wrestle skills.

\subsubsection{Jump Up (Agility)}
\par If the player declares any Action while Prone, other than a Block Action, they may stand up for free. The player may also declare a Block Action while Prone, which requires an Agility roll with a +2 modifier to see if they can complete the Action. On a failed roll, the Block Action is wasted and the player may not stand up.

\subsubsection{Kick (General)}
\par In order to use this skill the player must be set up on the pitch, but not in a wide zone or on the line of scrimmage, when their team kicks off. Because their kick is so accurate, you may choose to halve the number of squares that the ball scatters on kick-off, rounding down.

\subsubsection{Kick-Off Return (General)}
\par In order to use this skill the player must be set up on the pitch, but not in a wide zone or on the line of scrimmage, when their team receives the kick off. It allows the player to move up to 3 squares after the ball has been scattered. Only one player may use this skill each kick-off. This skill may not be used on a touchback and does not allow the player to cross into the opponent's half of the pitch.

\subsubsection{Leader (Passing)}
\par A team with one or more Leaders may add a Team Re-roll at the start of the game and at half time. This Leader re-roll may only be used so long as at least one player with the Leader skill is on the pitch.

\subsubsection{Leap (Agility)}
\par This player is allowed to jump to an empty square within 2 squares, even if they need to jump over another player from either team. Making a leap costs 2 MA. In order to make the leap, move the player to an eligible empty square (they do not have to dodge to leave their square), then make an Agility roll; no modifiers apply unless they have Very Long Legs. If the roll is successful then the jump is perfect and they may carry on moving. If they fail, they are Knocked Down in the square that they were leaping to, and the opposing coach makes an Armour roll. A player may only use the Leap skill once per turn.

\subsubsection{Loner (Extraordinary)}
\par A Loner must roll 4+ on a D6 before they may use a team re-roll; on a roll of 1-3 the original result stands but the team re-roll is lost.

\subsubsection{Mighty Blow (Strength)}
\par Add 1 to the Armour roll or the Injury roll when this player knocks an opponent down during a block. You may only modify one of the dice rolls. If this player uses Claws, you may not modify the Armour roll further with Mighty Blow.

\subsubsection{Multiple Block (Strength)}
\par If this player is adjacent to at least two opponents and declares a Block action, they may choose to throw blocks against two of them. Make each block in turn as normal, except that each defender's strength is increased by 2. The player cannot follow up after either block, and Multiple Block cannot be used together with Frenzy. To make the second block, the player must still be on their feet after the first block.

\subsubsection{Nerves of Steel (Passing)}
\par This player ignores modifiers for enemy tackle zones when they attempt to pass, catch or intercept.

\subsubsection{Pass (Passing)}
\par This player is allowed to re-roll the D6 if they throw an inaccurate pass or fumble.

\subsubsection{Prehensile Tail (Mutation)}
\par Opponents must subtract 1 from their roll if they attempt to dodge out of any of this player's tackle zones.

\subsubsection{Pro (General)}
\par Once per turn, a Pro is allowed to re-roll any dice roll they have made (other than Armour, Injury or Casualty rolls), even if they are Prone or Stunned. However, before the re-roll may be made, their coach must roll 4+ on a D6. On a roll of 1-3 the original result stands and may not be re-rolled. You can re-roll the Pro roll with a Team re-roll.

\subsubsection{Really Stupid (Extraordinary)}
\par Roll a D6 immediately after declaring an Action for this player. If the player has team-mates standing in adjacent squares who aren't Really Stupid, add 2 to the roll. Unless the result is 4+ the player can't do anything for the turn, and the player's team loses the declared Action for the turn. The player loses their tackle zones and may not catch, intercept, pass, assist on blocks or fouls, or voluntarily move until they manage a successful Really Stupid roll at the start of a future Action.

\subsubsection{Regeneration (Extraordinary)}
\par If this player suffers a Casualty, roll a D6 for Regeneration after the roll on the Casualty table and after any Apothecary roll. On a 4+, they do not suffer the casualty and are placed in the Reserves box instead. Regeneration rolls may not be re-rolled. Even if the roll is successful, the opposing team still gets the credit for the casualty when rolling for Star Player points.

\subsubsection{Right Stuff (Extraordinary)}
\par This player can be thrown by a team-mate with the Throw Team-Mate skill.

\subsubsection{Safe Throw (Passing)}
\par If a pass made by this player is ever intercepted, they may make an unmodified Agility roll; if it is successful then the interception is cancelled. In addition, if they fumble a pass on any roll other than a natural 1, they manage to keep hold of the ball instead of suffering a fumble; the pass does not continue and the team does not suffer a turnover.

\subsubsection{Shadowing (General)}
\par The player may use this skill when the active player on the opposing team moves out of any of their tackle zones for any reason. The opposing player rolls 2D6, adds their own MA and subtracts the Shadowing player's MA. If the final result is 7 or less, the player with Shadowing may move into the square vacated by the opposing player. They do not have to make any Dodge rolls when they make this move. A player may make any number of shadowing moves per turn. If a player has left the tackle zone of several players that have the Shadowing skill, then only one of them may attempt to shadow them.

\subsubsection{Side Step (Agility)}
\par This player may choose which square they are moved to when they are pushed back. Furthermore, they may choose to move to any adjacent square, not just the three squares normally available. The skill works even if the player is Knocked Down after the push back. However, the player may not use this skill if no adjacent squares are empty.

\subsubsection{Sneaky Git (Agility)}
\par During a Foul, this player is not ejected for rolling doubles on the Armour roll unless the roll was successful.

\subsubsection{Sprint (Agility)}
\par This player may attempt to move up to three extra squares when Going For It, rather than two.

\subsubsection{Stab (Extraordinary)}
\par This player may Stab instead of throwing a Block. Make an unmodified Armour roll; if this succeeds then the Injury roll is also unmodified (including by Niggling Injuries). If Stab is used as part of a Blitz, the player cannot continue moving after using it. Casualties caused by Stab do not count for Star Player points.

\subsubsection{Stand Firm (Strength)}
\par This player may choose not to be pushed back as the result of any block, including when Knocked Down. If a player is pushed back into a player with Stand Firm, neither player moves.

\subsubsection{Strip Ball (General)}
\par When this player blocks an opponent with the ball, applying a 'Pushed Back' or 'Defender Stumbles' result will cause the opponent to drop the ball in the square that they are pushed to, even if they are not Knocked Down.

\subsubsection{Strong Arm (Strength)}
\par This player may add 1 to the Agility roll when they pass to Short, Long or Long Bomb range.

\subsubsection{Stunty (Extraordinary)}
\par This player may ignore any enemy tackle zones on the square they are moving to when they make a Dodge roll, but must subtract 1 from the roll when passing the ball. In addition, the opponent may add 1 to any Injury roll they make for this player.

\subsubsection{Sure Feet (Agility)}
\par This player may re-roll the D6 if they are Knocked Down when trying to Go For It. They may only use the Sure Feet skill once per turn.

\subsubsection{Sure Hands (General)}
\par This player may re-roll the D6 if they fail to pick up the ball. In addition, the Strip Ball skill will not work against a player with Sure Hands.

\subsubsection{Tackle (General)}
\par Opposing players who are standing in any of this player's tackle zones are not allowed to use their Dodge skill if they attempt to dodge away. Opposing players may also not use their Dodge skill if this player throw a block at them and uses the Tackle skill.

\subsubsection{Take Root (Extraordinary)}
\par Roll a D6 immediately after declaring an Action for this player. On a roll of 1, the player “takes root”, and may not leave their square voluntarily, or be pushed back, until they are Knocked Down or placed Prone or the drive ends. This player may block adjacent players without following-up as part of a Block Action, but if they fail their Take Root roll as part of a Blitz Action they may not block that turn.  If they fail their Take Root roll when Prone, they may still roll to stand up.

\subsubsection{Tentacles (Mutation)}
\par This player may attempt to use this skill when an opposing player attempts to move out of any of their tackle zones. The opposing player rolls 2D6, adds their own player's ST and subtracts the tentacled player's ST. If the final result is 5 or less, then the moving player is held firm, and their action ends immediately (though their team does not suffer a turnover). If a player attempts to leave the tackle zone of several players that have the Tentacles ability, then only one of the opposing players may attempt to grab them.

\subsubsection{Thick Skull (Strength)}
\par This player treats a roll of 8 on the Injury table, after any modifiers have been applied, as a Stunned result rather than a KO'd result. This skill may be used even if the player is Prone or Stunned.

\subsubsection{Throw Team-Mate (Extraordinary)}
\par This player has the ability to throw a team-mate, including if the team-mate is holding the ball. The thrower must end the movement of their Pass Action standing next to the intended team-mate, who must have the Right Stuff and be standing.
\par If this player is Always Hungry, roll a D6 after they have finished moving but before they throw their team-mate. On a roll of 1 they attempt to eat them. Roll the D6 again: a second 1 kills the victim without any opportunity for recovery (if they had the ball it will scatter once). If the second roll is 2-6, treat the throw as fumbled; fumble the team-mate as normal.
\par The pass is worked out generally the same as throwing the ball, except the player must subtract 1 from the Agility roll, no interception may be attempted, and a Short Pass is the maximum range.
\par If the pass is fumbled, it is not automatically a turnover, and the teammate must make a landing roll (see below) for the square they originally occupied.
\par If the pass is not fumbled, even accurate passes are treated as inaccurate, scattering the player three times. If the thrown player scatters off the pitch, they are beaten up by the crowd. If they land on another player, treat that player landed on as Knocked Down and roll for Armour (even if already Prone or Stunned), and then the thrown player will scatter one more square. If this would mean landing on another player, continue to scatter as necessary (i.e. they cannot land on more than one player).
\par When the thrown player ends up in an unoccupied square, they must make a landing roll, unless they landed on another player during the throw. A landing roll is an Agility roll with a -1 modifier for each opposing player's tackle zone on the square they land in. If they pass the roll they land on their feet. If the landing roll is failed, or they landed on another player during the throw, they are placed Prone and must pass an Armour roll to avoid injury. If the player is not injured during their landing they may take an Action later this turn if they have not already done so. A failed landing roll or landing in the crowd does not cause a turnover, unless they were holding the ball.

\subsubsection{Two Heads (Mutation)}
\par Add 1 to all Dodge rolls this player makes.

\subsubsection{Very Long Legs (Mutation)}
\par Add 1 to the Agility roll whenever this player attempts to intercept or Leap. In addition, the Safe Throw skill may not be used to affect any Interception rolls made by this player.

\subsubsection{Wild Animal (Extraordinary)}
\par Roll a D6 immediately after declaring an Action for this player, adding 2 to the roll if taking a Block or Blitz. On a result of 1-3,  the Action is wasted.

\subsubsection{Wrestle (General)}
\par If this player blocks or is blocked and the result is 'Both Down', they may choose to wrestle both players to the ground. Both players are placed Prone in their respective squares, even if one or both have the Block skill. Do not make Armour rolls for either player. Use of this skill does not cause a turnover unless the active player was holding the ball.

\end{multicols}

\subsection{Skills by category}

\begin{multicols}{3}

\begin{samepage}
\subsubsection{General}
\begin{itemize}
\item[] Block
\item[] Dauntless
\item[] Dirty Player
\item[] Fend
\item[] Frenzy
\item[] Kick
\item[] Kick-Off Return
\item[] Pro
\item[] Shadowing
\item[] Strip Ball
\item[] Sure Hands
\item[] Tackle
\item[] Wrestle
\end{itemize}
\end{samepage}

\begin{samepage}
\subsubsection{Agility}
\begin{itemize}
\item[] Catch
\item[] Diving Catch
\item[] Diving Tackle
\item[] Dodge
\item[] Jump Up
\item[] Leap
\item[] Side Step
\item[] Sneaky Git
\item[] Sprint
\item[] Sure Feet
\end{itemize}
\end{samepage}

\columnbreak

\begin{samepage}
\subsubsection{Strength}
\begin{itemize}
\item[] Break Tackle
\item[] Grab
\item[] Guard
\item[] Juggernaut
\item[] Mighty Blow
\item[] Multiple Block
\item[] Stand Firm
\item[] Strong Arm
\item[] Thick Skull
\end{itemize}
\end{samepage}

\begin{samepage}
\subsubsection{Passing}
\begin{itemize}
\item[] Accurate
\item[] Dump-Off
\item[] Hail Mary Pass
\item[] Leader
\item[] Nerves of Steel
\item[] Pass
\item[] Safe Throw
\end{itemize}
\end{samepage}

\columnbreak

\begin{samepage}
\subsubsection{Mutation}
\begin{itemize}
\item[] Big Hand
\item[] Claws
\item[] Disturbing Presence
\item[] Extra Arms
\item[] Foul Appearance
\item[] Horns
\item[] Prehensile Tail
\item[] Tentacles
\item[] Two Heads
\item[] Very Long Legs
\end{itemize}
\end{samepage}

\begin{samepage}
\subsubsection{Extraordinary}
\begin{itemize}
\item[] Always Hungry
\item[] Bonehead
\item[] Decay
\item[] Loner
\item[] Really Stupid
\item[] Regeneration
\item[] Right Stuff
\item[] Stab
\item[] Stunty
\item[] Take Root
\item[] Throw Team-Mate
\item[] Wild Animal
\end{itemize}
\end{samepage}

\end{multicols}
